### 2018-05-20 manuscript/visualdesign.tex
abstract, title updated

\section{Idea}

Classification method, flow clustering method, Semantic representation.

The key of our work is to align the analysis of urban dynamics with the available of individual characteristics.

Problem to solve: 
\begin{itemize}
\item \textit{Groups of people}: multiple attributes, semantic understanding, loose attribute boundary
\item \textit{Urban Dynamics of People Group}: where those people go and how they access the ... in a city. the patterns of behaviour classified by different social characteristics.  
\end{itemize}

@@

@@

Face... Data-driven inforgraphics~\cite{}.

>>>>

@@

Glyph design is

@@

Face... Data-driven inforgraphics~\cite{}. Following the idea of Chernoff Face~\cite{1973}, we utilize that we better know the perceptual figures well before we use them. By designing different visual dimensions, knowned as a type of glyph, a graphical representation of people with specific social characteristics. Those visual profiles are intended for intutive visual understanding and clustering.
